Astrophysical calibration of gravitational-wave detectors

### 2015-04-24 docs/cosmic_cal.tex
Some minor changes in discussion about calibration

%\documentclass[12pt]{iopart}
%\newcommand{\gguide}{{\it Preparing graphics for IOP journals}}
%Uncomment next line if AMS fonts required
%\usepackage{iopams}  
%\usepackage {amsmath}
%\usepackage {amssymb}
%\usepackage {amsfonts}
%\usepackage {amsthm}
%\usepackage {mathrsfs}
%\usepackage {natbib}
%\usepackage {latexsym}
%\usepackage {graphicx}
%\usepackage {dsfont}
%\usepackage {times}
%\usepackage {txfonts}
%\usepackage {rotating}
%\usepackage {wasysym}
%\usepackage {multirow}
%\usepackage {hhline}
\usepackage {hyperref}
%\usepackage {color}
\usepackage {bm}
%\usepackage{appendix}
\usepackage{acronym}
%\usepackage{dcolumn}   % needed for some tables
\usepackage {url}
%\usepackage[normalem]{ulem}   % temporal one in draft.

@@

% Describe our model for the calibration
In this work the calibration correction factor used throughout is simply a scale
factor, $s$. This effects the data set collected by a simple multiplication:
%
\begin{equation}\label{eq:scaledata}
  h(t) = s\times h_{\mathrm{m}}(t)
\end{equation}
%
where $h_{\mathrm{m}}(t)$ is the measured detector strain, and
$h(t)$ is the exact perfectly calibrated strain. A description of the
collected data is given in Section~\ref{sec:cbc}. The scale factor being
parameterised, $s$, represents all known sources of error in the system. This
is not entirely realistic as $s$ is known to be a function of frequency.
Testing a more realistic calibration error is work to be done in the
future.~\cm{Need to clean this up and expand the discussion}

>>>>

%\documentclass[12pt]{iopart}
%\newcommand{\gguide}{{\it Preparing graphics for IOP journals}}
%Uncomment next line if AMS fonts required
%\usepackage{iopams}  
%\usepackage {amsmath}
%\usepackage {amssymb}
%\usepackage {amsfonts}
%\usepackage {amsthm}
%\usepackage {mathrsfs}
%\usepackage {natbib}
%\usepackage {latexsym}
%\usepackage {graphicx}
%\usepackage {dsfont}
%\usepackage {times}
%\usepackage {txfonts}
%\usepackage {rotating}
%\usepackage {wasysym}
%\usepackage {multirow}
%\usepackage {hhline}
\usepackage {hyperref}
%\usepackage {color}
\usepackage {bm}
%\usepackage{appendix}
\usepackage{acronym}
%\usepackage{dcolumn}   % needed for some tables
\usepackage {url}
\usepackage[normalem]{ulem}   % temporal one in draft.

@@

\MP{The gravitational wave strain is measured through the differential arm length changes
of the interferometer via $h = \Delta L(f) / L$, where $L$ is the total arm length.
Calibration is required to relate the actual measured interferometer error signal ouptut
$e(f)$ to this differential arm length $\Delta L$. This relation
is known as the length response function, $R(f,t)$, defined such that
\begin{equation}
\Delta L(f) = R(f,t) e(f),
\end{equation}
where $R$ various slowly in time (in comparison to transient signal timescales).
Calculation of $R$ requires the measurement of various functions within a control feedback loop
(see \cite{Vitale:2012} for a brief overview of this), which are subject to
uncertainties. In this study we will assume an estimate of $R$ is available (although
in theory we could take on the role of estimating $R$ itself), but that it differs from the
truth through some unknown scale factor, $s$, so that
\begin{equation}
h_{\rm true}(f) = s h_{\rm measured}(f) = s \frac{R(f,t) e(f)}{L}.
\end{equation}
In this analysis we will simplify the situation by assuming that $s$ is a constant with
respect to frequency, but in future studies that assumption could be dropped and $s$
could take some functional form with respect to $f$.
}

% Describe our model for the calibration
In this work the calibration correction factor used throughout is simply a scale
factor, $s$. This effects the data set collected by a simple multiplication:
%
\begin{equation}\label{eq:scaledata}
  h(t) = s\times h_{\mathrm{m}}(t)
\end{equation}
%
where $h_{\mathrm{m}}(t)$ is the measured detector strain, and
$h(t)$ is the exact perfectly calibrated strain. \sout{A description of the
collected data is given in Section~\ref{sec:cbc}}. The scale factor being
parameterised, $s$, represents all known sources of error in the system. This
is not entirely realistic as $s$ is known to be a function of frequency.
Testing a more realistic calibration error is work to be done in the
future.~\cm{Need to clean this up and expand the discussion}
